---
title: "setting_up_R"
author: "LC"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Setting up R Pro

**On Fiji** 
1) Create a new directory for workflow and version control
    mkdir ~/R/<Directory_Name> 
    posit_libs -> R profile
    x86_64-pc-linux-gnu-library --> .Renviron info
    
2) Create a .Renviron and .Rprofile in our home directory.
.Renviron = Contains the devtoolset-10 line appended to your PATH
    nano .Renviron
      PATH=/opt/rh/devtoolset-10/root/bin:/usr/bin:$PATH
.Rprofile = Directory for workflow & version control 
    nano .Rprofile
      .libPaths(c("/Users/laca6459/R/Posit_libs", "/opt/R/4.3.1/lib/R/library/", .libPaths()))

**Launching R Studio Pro**
1) Request the Small resource profile (4 CPUs and 32GB RAM)
2) Queue can either be "sandbox" or "highmem"

**On R Studio Pro**
1) Assign library directory created to .Rprofile

#Curl - Newest version not supported aka potential source of error
```{r setup, include=FALSE}
install.packages("remotes")
library(remotes)
install_version("curl", "5.2.3") #Needed to set ___ to a different version in order for it to flow correctly. 
```

# CRAN Repository Download - comprehensive R archive network
```{r setup, include=FALSE}
install.package("tidyverse") #install a package
install.package("dplyr")
install.package("IRanges")
install.package("ggplot2")
install.package("purrr")
install.package("readr")
install.package("tibble")
install.package("tidyr")
```

# Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #clean, logical and readable coding
library(dplyr) #Grammar of Data Manipulation
library(ggplot2) #Customize Plots, color is a vector so you can scale graphs big
library(purrr) #Enhances R's programming functions
library(readr) #Read csv and tsv 
library(tibble) #Reshaping data frame
library(tidyr) #Convert between long and wide data frames
library(magrittr) #Used for pipe functions
library(pheatmap) #Makes pretty heat maps
library(textshape) #Shape text on a plot
library(Rcpp) #Integration of R and C++
library(matrixStats) #Take matrix tables to use for stats
```

# Bioconductor Repository Download (v 3.18) - Geared to Bioinformatics
```{r setup, include=FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.18") #change version

BiocManager::install("rtracklayer") #install package
```

# Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DESeq2) #Differential Gene Expression Data based on negative bionomial distributions
library(IRanges) #Integer range manipulation
library(rtracklayer) #Interface to Genome Annotation and Genome Browsers
```
